---
title: "Cryptocurrency Market Capitalization"
output:
  html_notebook:
    code_folding: hide
    theme: spacelab
    includes:
      in_header: google-analytics.js
runtime: shiny
---

```{r setup, warning=FALSE}

library(shiny)
library(knitr)
library(treemap)

library(rbcb)
library(coinmarketcapr)

# disable scientific notation and show only 3 digits
options(scipen=999, digits = 3)

getCurrencies <- reactive({
  
  currencies <- tryCatch({
    get_all_currencies(Sys.Date())
  }, error = function(e) {
    get_all_currencies(Sys.Date() - 1)
  })
  
  currencies <- currencies[currencies$symbol %in%
                             c("ARS", "USD", "EUR", "GBP"),]
  
  return (currencies[,c("symbol", "bid", "ask")])
  
})

getCryptoMarketToday <- reactive({
  
  market_today <- get_marketcap_ticker_all()
  
  return (market_today)
})

```

## Currencies

The following table summarizes **market value** of the main currencies, compared to the Brazillian Real (BRL), according to data extracted from the Brazillian Central Bank. The bid-ask spread is the amount by which the ask price exceeds the bid price for the currency in the Brazillian market.

```{r, warning=FALSE}

renderDataTable({
  
  currencies <- getCurrencies()
  
  colnames(currencies) <- c("Symbol", "Bid", "Ask")
  
  return (currencies)
  
}, options = list(searching = FALSE,
                  paging = FALSE)
)

```

## Cryptocurrencies

The following table summarizes the top 10 cryptocurrencies by market capitalization, according to CoinMarketCap. The tree map shows a nice visualization of this capitalization.

```{r, warning=FALSE}

renderDataTable({
  
  currencies <- getCurrencies()
  
  usd <- as.numeric(currencies[currencies$symbol == "USD",c("bid")])
  
  market_today <- getCryptoMarketToday()
  
  market_today$price_usd <- as.numeric(market_today$price_usd)
  market_today$price_brl <- market_today$price_usd * usd

  market_today <- market_today[,c("name", "symbol", "rank", "price_usd", "price_brl")]
  colnames(market_today) <- c("Name", "Symbol", "Rank", "USD", "BRL")

  return (head(market_today, 10))

}, options = list(searching = FALSE,
                  paging = FALSE)
)

```

```{r, warning=FALSE}
renderPlot({
  
  market_today <- getCryptoMarketToday()
  
  df1 <- na.omit(market_today[,c('symbol','market_cap_usd')])
  
  df1$market_cap_usd <- as.numeric(df1$market_cap_usd)
  
  df1$formatted_market_cap <- paste0(df1$symbol,'\n','$',
                                     format(df1$market_cap_usd,big.mark = ',',
                                            scientific = F, trim = T))
  treemap(df1, index = 'formatted_market_cap',
          vSize = 'market_cap_usd',
          title = 'Cryptocurrency Market Cap',
          fontsize.labels=c(12, 8), palette='RdYlGn')
})

```